TITLE

### 2021-02-25 outputs/Paper.Rmd
update t test

The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
```

### Revenue distributions group by restaurant size
```{r revenue_distribution, echo=FALSE}

library(ggplot2)
library(ggthemes)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

>>>>

The first six rows of raw data is shown in the Table1. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
### T-Test
```{r ttest,echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()

```
The T Test is used to compare the sample mean of our Treated group and Control group. The goal is to determine whether the intervention has an effective effect on the treated group. Our hypothesis is the intervention will have positive impact towards the restaurant's revenue. [@kim2015t] The T test results is represented in the Table2(Table \@ref(tab:ttest)). The package **Broom**[@broom1] is used to clean the t test results and convert it into the dataframe. The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant).[@kim2015t] So we can 
interpret hypothesis not rejected which means the intervention has a significant effect on treated group.

### Revenue distributions group by restaurant size
```{r revenue_distribution, echo=FALSE}
library(ggplot2)
library(ggthemes)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )
```
